### 2016-05-20 paper/paper.tex
Moving TLS 1.3 to discussion
Ethics changes

Although not yet implemented, the current TLS 1.3 proposal appears to also have the
necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
Certificate Verify message includes a signature from the server over essentially
all prior handshake messages, including the Client Hello that contains the
\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
servers with only minor modifications.

@@

%Jumping the gun on PAY\_TO\_DDOS transactions before they find their way into the block chain
%could be weird. Especially if people start only inserting them as they solve the puzzle.
\todo{Talk about TLS 1.3, signing client controlled values}

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin, and keep the source of our proof of concept
closed. We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use.

>>>>

@@

%Jumping the gun on PAY\_TO\_DDOS transactions before they find their way into the block chain
%could be weird. Especially if people start only inserting them as they solve the puzzle.

Although not yet implemented, the current TLS 1.3 proposal appears to also have the
necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
Certificate Verify message includes a signature from the server over essentially
all prior handshake messages, including the Client Hello that contains the
\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
servers with only minor modifications. This should be considered in the design of 
TLS 1.3 due to the long life of TLS implementations.

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin, and keep the source of our proof-of-concept
closed. We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
beyond just DDoSCoin.
